---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# accordionNav

<!-- badges: start -->
<!-- badges: end -->

This project showcases an easy way to create menu items stored within a navigation dropdown menu in bslib. 

## Installation

You can install the development version of accordionNav from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("B-Klaver/accordionNav")
```

## Example

Set up your menu using nested lists:

```{r setup, eval = FALSE}
library(accordionNav)

## set up menu list

domain_list <- list(
  "Domain 1" = list(
    "Sub-domain 1.1",
    "Sub-domain 1.2"
  ),
  "Domain 2" = list(
    "Sub-domain 2.1"
  ),
  "Domain 3" = list(
    "Sub-domain 3.1",
    "Sub-domain 3.2",
    "Sub-domain 3.3"
  )
)

```

Now you can use this menu list within a sidebar UI using the `accordionTabset()` function. In addition, create a `navset_hidden()`
bin and place your panels that you'd like to show with `nav_panel_hidden()`. The values should be set to the name of the menu item it relates to:

```{r ui, eval = FALSE}

ui <- bslib::page_sidebar(
  title = "Accordion Navigation Example",
  class = "bslib-page-dashboard",
  sidebar = bslib::sidebar(
    accordionTabset(
      "accord_select", 
      domain_list,
      class = "link-body-emphasis d-inline-flex text-decoration-none mb-3 rounded w-100"
    )
  ),
  bslib::navset_hidden(
    id = "hidden_tabs",
    bslib::nav_panel_hidden(
      value = domain_list$`Domain 1`[[1]],
      "Panel 1.1 content"
    ),
    bslib::nav_panel_hidden(
      value = domain_list$`Domain 1`[[2]],
      "Panel 1.2 content"
    ),
    bslib::nav_panel_hidden(
      value = domain_list$`Domain 2`[[1]],
      "Panel 2.1 content"
    ),
    bslib::nav_panel_hidden(
      value = domain_list$`Domain 3`[[1]],
      "Panel 3.1 content"
    ),
    bslib::nav_panel_hidden(
      value = domain_list$`Domain 3`[[2]],
      "Panel 3.2 content"
    ),
    bslib::nav_panel_hidden(
      value = domain_list$`Domain 3`[[3]],
      "Panel 3.3 content"
    )
  )
)

```


Easily link the accordion tabset buttons to the hidden nav panels using the `accordionPanelSelect()` function:

```{r server, eval = FALSE}

server <- function(input, output, session) {
  
  accordionPanelSelect(
    input, 
    session,
    panel_id = "hidden_tabs",
    accordion_id = "accord_select",
    menu_list = domain_list
  )
  
}

```